Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
JS distances in application

Figure \ref{fig:opt-cluster-tsne-jsd} The $sindex$ is plotted against the number of clusters for clustering based on JS-based (JS-NQT) distances in Figure \ref{fig:opt-cluster-tsne-jsd}. The $sindex$ falls from around $0.56$ when $k=3$ to $0.54$ when $k$ increases. In our study, we use $k=4, 5$. Figure \ref{fig:groups-4and5} depicts the summarized distributions across $4$ and $5$ clusters in (a) and (b) respectively, and assists in characterizing each cluster. In the following plots, the median is shown by a line, and the shaded region shows the area between the  $25^{th}$ and $75^{th}$ percentiles. Groups A-1, A-2, and A-3 have profiles that correspond to B-1, B-2, and B-3 respectively. B-2 (id: 4-9 in Figure \ref{fig:hod-ind-group-png}) and B-1 (id: 21-24) have a $hod$ pattern with a typical morning and evening peak, whereas the other groups have no distinct pattern or high variability throughout the day. A-4 is subdivided into B-4 and B-5, each of which has a distinct shape across $moy$ and $wnwd$. B-4 (id: 16-20) is distinguished by higher energy consumption in the first few months of the year and greater variability in weekend usage. B-5 (id: 1-3) has higher consumption in the middle of the year (winter months) and a similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a $moy$ profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals. It may be worthwhile to compare Figures \ref{fig:opt-cluster-tsne-jsd} and \ref{fig:hod-ind-group-png} to see if the summarized distributions across groups accurately characterized the groupings. If it has, then the majority of the members of the group should have a similar profile.

@@

>>>>

<!--### JS-NQT and JS-RS-->

<!--Figure \ref{fig:opt-cluster-tsne-jsd} The $sindex$ is plotted against the number of clusters for clustering based on JS-based (JS-NQT) distances in Figure \ref{fig:opt-cluster-tsne-jsd}. The $sindex$ falls from around $0.56$ when $k=3$ to $0.54$ when $k$ increases. In our study, we use $k=4, 5$.--> Figure \ref{fig:groups-4and5} displays the summarized distributions across $4$ and $5$ clusters in (a) and (b) respectively, and helps to characterize each cluster. In the quantile plots the line represents the median, and the region shows the area between the  $25^{th}$ and $75^{th}$ percentiles. The only difference between the four and five cluster solution is that A-4 divides further into B-4 and B-5. This additional division makes a clearer clustering, because it resolves the heterogeneity in $moy$ creating a group (B-5, customers 1-3) which has a winter peak in usage, and a group (B-4, customers 16-20) which has a start of the year peak in usage.  B-2 (customers 4-9) and B-1 (customers 21-24) have distinctive $hod$ patterns but are both heterogeneous in $moy$ and $wnwd$. B-3 (customers 10-15) has peak usage at the end of the year, but is heterogeneous on $hod$ and $wdwn$. This clustering almost agrees with the clusters visible in the t-SNE plot.

<!-- A-4 is subdivided into B-4 and B-5, each of which has a distinct shape across $moy$ and $wnwd$. B-4 (id: 16-20) is distinguished by higher energy consumption in the first few months of the year and greater variability in weekend usage. B-5 (id: 1-3) has higher consumption in the middle of the year (winter months) and a similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a $moy$ profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals. It may be worthwhile to compare Figures \ref{fig:opt-cluster-tsne-jsd} and \ref{fig:hod-ind-group-png} to see if the summarized distributions across groups accurately characterized the groupings. If it has, then the majority of the members of the group should have a similar profile.-->

@@

<!--### WPD-->
